Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-13 paper/galsize_paper.tex
Added paragraph to Future Work making clear the importance of forward-modeling B/T for self-consistent treatment of 2d vs. 3d sizes

>>>>

In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and sizes together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge. Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques. For example, it is common to ``deproject" two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately. The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately, and for each model galaxy the projected size can be computed self-consistently with the modeled value of ${\rm B/T}.$ This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites having smaller sizes than centrals is due to differences in ${\rm B/T}.$
